Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks

### 2016-10-15 paper.tex
Abstract reviewev by Xavi

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}        % equations

@@

    This work proposes a simple pipeline to classify and temporally localize activities in untrimmed videos. Our system uses features from a 3D Convolutional Neural Network (3D-CNN) as input to train a a recurrent neural network (RNN) that learns to classify each segment of the video. After training, we post-process the output of the RNN to be able to both assign a single activity label to each video and temporally localize when that activity happens within the input video. We find that our system can achieve competitive results in both tasks with a simple architecture composed. We evaluate our method in the ActivityNet Challenge 2016, achieving a 0.00 mAP and a 0.00 mAP in the classification and detection tasks, respectively. Our code and models can be found at: \url{ https://github.com/imatge-upc/activitynet-2016-cvprw}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}        % equations
\usepackage{color}

@@

    This work proposes a simple pipeline to classify and temporally localize activities in untrimmed videos. Our system uses features from a 3D Convolutional Neural Network (3D-CNN) as input to train a a recurrent neural network (RNN) that learns to classify video clips of 16 frames. After clip prediction, we post-process the output of the RNN to assign a single activity label to each video, and determine the temporal boundaries of the activity within the video. We show how our system can achieve competitive results in both tasks with a simple architecture. We evaluate our method in the ActivityNet Challenge 2016, achieving a 0.00 mAP and a 0.00 mAP in the classification and detection tasks, respectively. Our code and models are publicly acailable at at: \url{ https://github.com/imatge-upc/activitynet-2016-cvprw}
